---
title: "Untitled"
author: "Olga Lukasevych"
date: "October 18, 2018"
output: ioslides_presentation
width: 1440
height: 900
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## Quantity of the highest risk volcano in countries

```{r high risk, echo = FALSE,warning=FALSE,message=FALSE}
df <- read.csv("data/volcano.csv",stringsAsFactors = FALSE)
#air <- read.csv("data/avia_tf_aca_1_Data.csv",stringsAsFactors = FALSE)
library(plotly)
library(tidyverse)
risk3 <- df %>% filter(risk=="3")
z <- risk3 %>% count(risk,Country) %>% arrange(desc(n)) %>% top_n(5)
plot_ly(z,x=factor(z$Country,levels=z$Country),y=z$n,type = "bar")
```

##
```{r Indonesia,echo = FALSE,warning=FALSE,message=FALSE}
##open data url and create data directory, download data
if(!file.exists("./data")){dir.create("./data")}
fileUrl <- "http://api.worldbank.org/v2/en/indicator/AG.LND.TOTL.K2?downloadformat=csv"
download.file(fileUrl,destfile="./data/Dataset.zip",mode = "wb")

##unzip downloaded file
DatasetFiles<-unzip("./data/Dataset.zip" , exdir = "data")
area <-read.delim (DatasetFiles[2],skip = 3,header = 3)

```