---
title: "Untitled"
author: "Olga Lukasevych"
date: "October 18, 2018"
output:
  ioslides_presentation: default
  slidy_presentation: default
height: 900
width: 1440
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

A comprehensive set of information on global volcanic hazard, historical events, population exposure, vulnerability, and impact has been provided to GAR15 by Global Volcano Model (GVM) and The International Association of Volcanology and Chemistry of the Earth’s Interior (IAVCEI). This work is the first of its kind in global coverage and level of contribution from a wide network of experts and institutions around the world.https://data.humdata.org/dataset/volcano-population-exposure-index-gvm

## Quantity of the highest risk volcano in countries

```{r high risk, echo = FALSE,warning=FALSE,message=FALSE}
df <- read.csv("data/volcano.csv",stringsAsFactors = FALSE)
#air <- read.csv("data/avia_tf_aca_1_Data.csv",stringsAsFactors = FALSE)
library(plotly)
library(tidyverse)
risk3 <- df %>% filter(risk=="3")
z <- risk3 %>% count(risk,Country) %>% arrange(desc(n)) %>% top_n(5)
plot_ly(z,x=factor(z$Country,levels=z$Country),y=z$n,type = "bar")
```

##
```{r Indonesia,echo = FALSE,warning=FALSE,message=FALSE}
risk3 <- risk3 %>% filter(Country=="Indonesia")
# geo styling
g <- list(
        scope = 'asia',
        #projection = list(type = 'albers indonesia'),
        showland = TRUE,
        center = list(lon=median(risk3$Longitude),lat=median(risk3$Latitude)),
        landcolor = toRGB("gray95"),
        subunitcolor = toRGB("gray85"),
        countrycolor = toRGB("gray85"),
        countrywidth = 1,
        subunitwidth = 0.5
)

p <- plot_geo(risk3, lat = ~Latitude, lon = ~Longitude) %>%
        add_markers(
                text = ~V_Name) %>% 
               
        #colorbar(title = "Incoming flights<br />February 2011") %>%
        layout(
                title = 'Indonesia Volcanos',
                geo = g
        )
p
  
```